Notes on Wide Gap

### 2016-05-13 paper/wide_gap_notes.tex
coarse search at Pm = 1E-4
fixed typo in B field flux function plot

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../../weakly_nonlinear_mri/python/widegap/figures/u_near_threshold_test}
\caption{Wide-gap first-order velocity perturbations near threshold. Unnormalized. This is with Q = 0.05, Rm = 0.85, but we now know that critical parameters are closer to Rm = 0.845, Q = 0.006 (finer grid running now).
\label{fig:firstorder_u}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../../weakly_nonlinear_mri/python/widegap/figures/B_near_threshold_test}
\caption{Wide-gap first-order B-field perturbations near threshold. Unnormalized. This is with Q = 0.05, Rm = 0.85, but we now know that critical parameters are closer to Rm = 0.845, Q = 0.006 (finer grid running now).
\label{fig:firstorder_B}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../../weakly_nonlinear_mri/python/widegap/figures/N2_test}
\caption{N2 from unnormalized lower-order components. This is with Rm = 0.845, Q = 0.006. Black = real, teal = imaginary. Why is psi not zero at the boundaries?
\label{fig:firstorder_B}}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../../weakly_nonlinear_mri/python/widegap/figures/u_near_threshold_test_critical}
\caption{Wide-gap first-order velocity perturbations near threshold. Unnormalized. This is with Rm = 0.845, Q = 0.006.
\label{fig:firstorder_u}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../../weakly_nonlinear_mri/python/widegap/figures/B_near_threshold_test_critical}
\caption{Wide-gap first-order B-field perturbations near threshold. Unnormalized. This is with Rm = 0.845, Q = 0.006.
\label{fig:firstorder_B}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../../weakly_nonlinear_mri/python/widegap/figures/firstorderperturbations_test}
\caption{First order perturbations, Rm = 0.845, Q = 0.006.
\label{fig:firstorder_all}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../../weakly_nonlinear_mri/python/widegap/figures/N2_test}
\caption{N2 from unnormalized lower-order components. This is with Rm = 0.845, Q = 0.006. Black = real, teal = imaginary. Why is psi not zero at the boundaries? Assuming it's because of the additional B advective term, not present in the thin-gap.
\label{fig:N2}}
\end{figure}
